Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 4

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematics (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
	Huang2013a, Spavone2017}.
	Although this phenomenon was well-documented, clear evidence of mass-dependent
	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
	ellipticity profiles has not been identified.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the projected 
	ellipticity profiles and their correlations with the kinematic of stars and 
	merging history have not been well explored. 
    \jenny{these sentences seem like an afterthought, maybe more natural before the main
    results of the paragraph?}
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

>>>>

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematics (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
    We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
	As expected, the ellipticity profile from image stacking method tends to be 
	shallower than the HSC one.  
	Uncertainties in aligning galaxies before stacking and the intrinsic isophotal 
	twist can lead to this effect.

	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
	Huang2013a, Spavone2017}.
	Although this phenomenon was well-documented, clear evidence of mass-dependent
	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
	ellipticity profiles has not been identified.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the 
	projected ellipticity profiles and their correlations with the kinematic of 
	stars and merging history have not been well explored.
